---
title             : "Detection in Context, Exp. 2 (prev. 4) - pre-registration document"
shorttitle        : "Detection in Context, Exp. 2 (prev. 4) - pre-registration document"

author: 
  - name          : "Matan Mazor"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Malet Street, London WC1E 7HX"
    email         : "mtnmzor@gmail.com"
  #   role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
  #     - Conceptualization
  #     - Writing - Original Draft Preparation
    
  - name          : "Clare Press"
    affiliation   : "1,2"
    # role:
    #   - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Birkbeck, University of London"
  - id            : "2"
    institution   : "Wellcome Centre for Human Neuroimaging, UCL"


abstract: |
  
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "detection, absence, presence"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : word_document
---

```{r setup, include = FALSE}
library('groundhog')
groundhog.library(
  c(
    'papaja',
    'tidyverse'
  ), "2023-12-01"
)
r_refs("r-references.bib")
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "",warning=F,echo=F,message=F,cache=T)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load-and-process}
E2.raw_df <- read_csv('../experiments/Exp2rows/data/jatos_resultfiles_batch1/all_data.csv') %>%
  filter(frame_index==0)%>%
  mutate(subj_id=PROLIFIC_PID,
         correct = as.numeric(correct),
         RT = as.numeric(RT),
         present=as.numeric(present),
         resp = response==presence_key,
         confidence = 0.5+confidence/2)  

E2.low_accuracy <- E2.raw_df %>%
  filter(test_part=='test1' | test_part=='test2') %>%
  group_by(subj_id) %>%
  summarise(
    accuracy = mean(correct)) %>%
  filter(accuracy<0.5) %>%
  pull(subj_id)

E2.too_slow <- E2.raw_df %>%
  filter(test_part=='test1' | test_part=='test2') %>%
  group_by(subj_id) %>%
  summarise(
    third_quartile_RT = quantile(RT,0.75)) %>%
  filter(third_quartile_RT>5000) %>%
  pull(subj_id)

E2.too_slow <- E2.raw_df %>%
  filter(test_part=='test1' | test_part=='test2') %>%
  group_by(subj_id) %>%
  summarise(
    third_quartile_RT = quantile(RT,0.75)) %>%
  filter(third_quartile_RT>5000) %>%
  pull(subj_id)

E2.too_fast <- E2.raw_df %>%
  filter(test_part=='test1' | test_part=='test2') %>%
  group_by(subj_id) %>%
  summarise(
    first_quartile_RT = quantile(RT,0.25)) %>%
  filter(first_quartile_RT<100) %>%
  pull(subj_id)

E2.to_exclude <- c(
  E2.low_accuracy,
  E2.too_slow,
  E2.too_fast
) %>% unique()

E2.df <- E2.raw_df %>%
  filter(!(subj_id %in% E2.to_exclude));
```

# Results

## Participants

`r E2.raw_df$subj_id%>%unique()%>%length()` participants took part. Participants were excluded if their accuracy fell below 50% (0 participants). We also excluded participants for having extremely fast (`r E2.too_fast%>%length()` participants) or slow (`r E2.too_slow%>%length()` participants) reaction times in one or more of the tasks (below 100 milliseconds or above 5 seconds in more than 25% of the trials). 

Trials with response time below 100 milliseconds (`r (E2.raw_df%>%filter(RT<100)%>%nrow()/E2.raw_df%>%filter(RT>0)%>%nrow())%>%printnum()` of all trials) or above 5 seconds (`r (E2.raw_df%>%filter(RT>5000)%>%nrow()/E2.raw_df%>%filter(RT>0)%>%nrow())%>%printnum()` of all trials) were excluded from the response-time analysis.

### Hypotheses and analysis plan

This study is designed to test the timing of decisions to terminate evidence accumulation in the absence of a target as a function of stimulus occlusion.

```{r H1, echo=FALSE, cache=TRUE}

E2.RT_by_resp <- E2.df %>%
  filter((test_part=='test1' | test_part=='test2') & RT>100 & RT<5000) %>%
  group_by(subj_id,resp) %>%
  summarise(RT=median(RT))%>%
  spread(resp,RT,sep='')%>%
  mutate(diff=respTRUE-respFALSE)


```

*Hypothesis 1 (PRESENCE/ABSENCE RESPONSE TIME)*: We tested the null hypothesis that response times are similar for target-absent and target-present responses, aiming to replicate the finding that decisions about the absence of a target are slower than decisions about its presence [@mazor2021metacognitive; @mazor2020distinct]. 

A paired t-test on the median individual level-response times revealed a significant difference (`r apa_print(E2.RT_by_resp%>%pull(diff)%>%t.test())$full_result`). 

```{r H2, echo=FALSE, cache=TRUE}

E2.RT_by_occlusion_in_presence_correct_only <- E2.df %>%
  filter((test_part=='test1' | test_part=='test2') & RT>100 & RT<5000 & resp & correct) %>%
  group_by(subj_id,hide_proportion) %>%
  summarise(RT=median(RT))%>%
  spread(hide_proportion,RT,sep='')%>%
  mutate(diff=hide_proportion0.1-hide_proportion0.35);

```

*Hypothesis 2 (OCCLUSION EFFECT IN PRESENCE)*: We tested the null hypothesis that target-present response times are similar when 2 or 6 pixel rows are occluded. 

A paired t-test on the median individual level-response times in correct trials only revealed a significant difference (`r apa_print(E2.RT_by_occlusion_in_presence_correct_only%>%pull(diff)%>%t.test())$full_result`).

```{r H3, echo=FALSE, cache=TRUE}

E2.RT_by_occlusion_in_absence_correct_only <- E2.df %>%
  filter((test_part=='test1' | test_part=='test2') & RT>100 & RT<5000 & !resp & correct) %>%
  group_by(subj_id,hide_proportion) %>%
  summarise(RT=median(RT))%>%
  spread(hide_proportion,RT,sep='')%>%
  mutate(diff=hide_proportion0.1-hide_proportion0.35);

```

*Hypothesis 3 (OCCLUSION EFFECT IN ABSENCE)*: We tested the null hypothesis that response times in target-absent responses are similar when 2 or 6 pixel rows are occluded. 

A paired t-test on the median individual level-response times in correct trials only revealed a null effect (`r apa_print(E2.RT_by_occlusion_in_absence_correct_only%>%pull(diff)%>%t.test())$full_result`).

```{r H4, echo=FALSE, cache=TRUE}

E2.RT_by_occlusion_and_response_correct_only <- merge(
  E2.RT_by_occlusion_in_presence_correct_only,
  E2.RT_by_occlusion_in_absence_correct_only,
  by= 'subj_id',
  suffixes = c('presence','absence')) %>%
  mutate(interaction = diffpresence-diffabsence);
```

*Hypothesis 4 (OCCLUSION RESPONSE INTERACTION)*: We tested the null hypothesis that the effect of occlusion on reaction time is similar in target-absent and target-present responses, by performing a group-level t-test on the subject-level contrast $(median(RT_{P,2})-median(RT_{P,6}))-(median(RT_{A,2})-median(RT_{A,6}))$ Where $P$ and $A$ stand for present and absent, and 2 and 6 represent the number of occluded rows. Here too, analysis was restricted to correct trials only.

We find a significant interaction (`r apa_print(E2.RT_by_occlusion_and_response_correct_only%>%pull(interaction)%>%t.test())$full_result`). 

```{r SDT, echo=FALSE, cache=TRUE}

E2.descriptives_by_occlusion<- E2.df %>%
  filter(test_part=='test1' | test_part=='test2') %>%
  mutate(resp = response==presence_key)%>%
  group_by(subj_id,hide_proportion) %>%
  summarise(accuracy=mean(correct),
            resp_bias=mean(resp),
            RT=median(RT),
            hit_rate = (sum(correct & present)+0.5)/(sum(present)+1),
            fa_rate = (sum(!correct & !present)+0.5)/(sum(!present)+1),
            d = qnorm(hit_rate)-qnorm(fa_rate),
            c = -0.5*(qnorm(hit_rate)+qnorm(fa_rate)))
```

*Hypothesis 5 (SENSITIVITY)*: We tested the null hypothesis that perceptual sensitivity (measured as $d'=z(H)-z(F)$) is equal as a function of the proportion of hidden pixels. To allow the extraction of d' for participants who committed no false-alarms or misses, we added 0.5 to miss, hit, false-alarm and correct rejection counts [@snodgrass1988pragmatics].

We find a significant drop in d' as a function of occlusion (`r apa_print(E2.descriptives_by_occlusion %>% group_by(subj_id) %>% summarise(diff=d[hide_proportion==0.10]-d[hide_proportion>0.3])%>%pull(diff)%>%t.test())$full_result`)

*Hypothesis 6 (CRITERION)*: We tested the null hypothesis that decision criterion (measured as $c=-0.5(z(H)+z(F))$) is unaffected by the proportion of hidden pixels. To allow the extraction of a decision criterion for participants who committed no false-alarms or misses, we added 0.5 to miss, hit, false-alarm and correct rejection counts [@snodgrass1988pragmatics].

We find a significantly more conservative criterion in high-occlusion trials (`r apa_print(E2.descriptives_by_occlusion %>% group_by(subj_id) %>% summarise(diff=c[hide_proportion==0.1]-c[hide_proportion>0.3])%>%pull(diff)%>%t.test())$full_result`).

```{r H7, echo=FALSE, cache=TRUE}

E2.confidence_by_resp_correct_only <- E2.df %>%
  filter((test_part=='test1' | test_part=='test2') & correct) %>%
  group_by(subj_id,resp) %>%
  summarise(confidence=mean(confidence, na.rm=T))%>%
  spread(resp,confidence,sep='')%>%
  mutate(diff=respTRUE-respFALSE)
```

*Hypothesis 7 (PRESENCE/ABSENCE CONFIDENCE)*: We tested the null hypothesis that confidence is similar in target-absent and target-present responses, aiming to replicate the finding that decisions about the absence of a target are accompanied by lower levels of subjective confidence than decisions about its presence [@mazor2021metacognitive; @mazor2020distinct].

A paired t-test on the mean individual-level confidence ratings from correct responses only revealed a significant difference  

(`r apa_print(E2.confidence_by_resp_correct_only%>%pull(diff)%>%t.test())$full_result`)

```{r H8, echo=FALSE, cache=TRUE}

E2.confidence_by_occlusion_in_presence_correct_only  <- E2.df %>%
  filter((test_part=='test1' | test_part=='test2') & resp & correct) %>%
  group_by(subj_id,hide_proportion) %>%
  summarise(confidence=mean(confidence, na.rm=T))%>%
  spread(hide_proportion,confidence,sep='')%>%
  mutate(diff=hide_proportion0.1-hide_proportion0.35);

```

*Hypothesis 8 (OCCLUSION CONFIDENCE EFFECT IN PRESENCE)*: We tested the null hypothesis that target-present confidence ratings are similar when 2 or 6 pixel rows are occluded.

A paired t-test on the mean individual-level confidence ratings in correct trials only revealed a significant effect (`r apa_print(E2.confidence_by_occlusion_in_presence_correct_only$diff%>%t.test())$full_result`).


```{r H9, echo=FALSE, cache=TRUE}

E2.confidence_by_occlusion_in_absence_correct_only <- E2.df %>%
  filter((test_part=='test1' | test_part=='test2') &!resp & correct) %>%
  group_by(subj_id,hide_proportion) %>%
  summarise(confidence=mean(confidence, na.rm=T))%>%
  spread(hide_proportion,confidence,sep='')%>%
  mutate(diff=hide_proportion0.1-hide_proportion0.35);

```
*Hypothesis 9 (OCCLUSION CONFIDENCE EFFECT IN ABSENCE)*: We tested the null hypothesis that target-absent confidence ratings are similar when 2 or 6 pixel rows are occluded. 

A paired t-test on the mean individual-level confidence ratings in correct trials only revealed a significant effect (`r apa_print(E2.confidence_by_occlusion_in_absence_correct_only$diff%>%t.test())$full_result`).


```{r H10, echo=FALSE, cache=TRUE}

E2.confidence_by_occlusion_and_response_correct_only <- merge(
  E2.confidence_by_occlusion_in_presence_correct_only,
  E2.confidence_by_occlusion_in_absence_correct_only,
  by= 'subj_id',
  suffixes = c('presence','absence')) %>%
  mutate(interaction = diffpresence-diffabsence);
```

*Hypothesis 10 (OCCLUSION RESPONSE INTERACTION ON CONFIDENCE)*: We tested the null hypothesis that the effect of occlusion on confidence is similar in target-absent and target-present responses, by performing a group-level t-test on the subject-level contrast $(mean(CONF_{P,2})-mean(CONF_{P,6}))-(mean(CONF_{A,2})-mean(CONF_{A,6}))$ Where $P$ and $A$ stand for present and absent, and 2 and 6 represent the number of occluded rows. Here too, analysis was restricted to correct trials only.

We find no significant interaction effect (`r apa_print(E2.confidence_by_occlusion_and_response_correct_only$interaction%>%t.test())$full_result`)

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
